NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/intro.tex
minor change

One recent advance in neural natural language process models is the
introduction of \emph{attention
  mechanisms}~\cite[for example]{bahdanau2014neural,VaswaniShazeerParmar2017}
(Section~\ref{sec:attention}). Intuitively, attention asks which parts of the
input are deemed more important for making a prediction. The attention is often represented via weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
%
%\shusen{seems repeated some of the previous points}
There have been many speculations on how attention works in various models.
Using the proposed tool, the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses. 
%we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention. And more importantly, we also allow the user to change prediction, where we apply a constrained optimization to find the least amount of parameter update to produce the user assign label. 
%Another word, 
%Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
Moreover, we propose to enhance the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
%
Finally, as discussed in Section~\ref{sec:grammarAttention}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate about the potential benefits of including the linguistic structure in the design of the attention component of the model.

>>>>

One recent advance in neural natural language process models is the
introduction of \emph{attention
  mechanisms}~\cite{bahdanau2014neural,VaswaniShazeerParmar2017}
(Section~\ref{sec:attention}). Intuitively, attention asks which parts of the
input are deemed more important for making a prediction. The attention is often represented via weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
%
%\shusen{seems repeated some of the previous points}
There have been many speculations on how attention works in various models.
Using the proposed tool, the domain experts can study how changes in sentence input, attention, or prediction affect each other, which helps them develop deeper intuitive and alternative hypotheses. 
%we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention. And more importantly, we also allow the user to change prediction, where we apply a constrained optimization to find the least amount of parameter update to produce the user assign label. 
%Another word, 
%Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
Moreover, we propose to enhance the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar-guided simplification of the visual representation.
%
Finally, as discussed in Section~\ref{sec:grammarAttention}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate about the potential benefits of including the linguistic structure in the design of the attention component of the model.
